NURM: a tool to locate numerical differences in pipelines

### 2019-10-16 paper.tex

\begin{tabular}{@{}llllll@{}}
\toprule
Type   & Number of Subjects  & Missing File(s)                                    \\ \midrule
type1  & 9                   & None                                               \\
type2  & 7                   & [``T1w", ``T2w"]                                   \\
type3  & 2                   & [``T1w"]                                           \\
type4  & 2                   & [``T2w"]                                           \\ \bottomrule
\end{tabular}
\begin{tablenotes}
     \small
     \item *Type refers to the topology type of the process tree of subjects.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\begin{figure}
\centering
  \includegraphics[width=\columnwidth]{images/pfs_heatmap.png}
  \caption{Heatmap of difference frequency of processes along with the sub-pipelines that introduce 
           differences among 20 subjects. The range between red and green colors show the most and 
           least frequency of processes respectively. Besides, the total number 
           of occurrences of each processes is represented in the bracket in each cell.}
  \label{fig:pfs_freq}
\end{figure}

@@

\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{images/segmentation.png} 
    \caption{Differences between FNIRT results of one subject from PreFreeSurfer 
    (checkerboard image \emph{T2w\_acpc\_to\_MNI\_nonli.nii.gz}) (CentOS6 vs. 
    CentOS7). Right images show the zoomed version part of the images marked 
    by the red rectangle.
    Here is 
    \href{https://raw.githubusercontent.com/ali4006/HCP-reproducibility-paper/master/images/brain_classification.gif}{the link}
    to the gif animation of the same images.
} 
    \label{fig:fnirt_result}
\end{figure}

@@

\begin{figure}
%  \includegraphics{brain\_classification}
\centering
  \includegraphics[width=\columnwidth]{images/brain_classification.png} 
  \caption{Heatmap binarized differences between brain segmentation results (file \emph{aseg.hires.mgz}) from 
          20 subjects in FreeSurfer (CentOS6 vs. CentOS7).} 
  \label{fig:tissue_class}
\end{figure}

@@

Although we identify the processes in the pipeline that create differences, 
the amplification of these differences should be quantified in the future works.
For this purpose, we can evaluate the final result after perturbing the identified 
processes in the pipeline iteratively.
As a result, the processes that amplify differences would have a significant effect on the results.

>>>>

\begin{tabular}{@{}llllll@{}}
\toprule
Type   & Number of Subjects  & Available Modalities                                         \\ \midrule
type1  & 9                   & [``T1w\_MPR1", ``T1w\_MPR2",                     \\
&  &                            ``T2w\_SPC1", ``T2w\_SPC2"]     \\
type2  & 8                   & [``T1w\_MPR1", ``T2w\_SPC1"]                                 \\
type3  & 1                   & [``T1w\_MPR1", ``T2w\_SPC1",   \\
&  &                            ``T2w\_SPC2"]                   \\
type4  & 2                   & [``T1w\_MPR1", ``T1w\_MPR2",   \\
&  &                            ``T2w\_SPC1"]                   \\ \bottomrule
\end{tabular}
\begin{tablenotes}
     \small
     \item *Type refers to the topology type of the process tree of subjects.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\begin{figure}
\centering
  \includegraphics[width=\columnwidth]{images/pfs_heatmap.png}
  \caption{Heatmap frequency of processes along with the sub-pipelines that introduce 
           differences among 20 subjects. The range between red and green colors shows the most and 
           least frequency of processes, respectively. 
           Each cell describes the frequency of the specific process in the sub-pipelines.        
           Each cell may split into multiple sub-cells when the specific process 
           called by different options (distinct process).
           Annotations represent `N [M] x Y" in which N is the percentage of the distinct process 
           that creates differences out of all M times that is occurred in that sub-pipeline. 
           Also, times Y shows the number of the distinct process with the same distribution.
           For example, the cell of process FLIRT in sub-pipeline AAve shows 10 distinct processes  
           with the frequency of 10 that introduce no differences.}
  \label{fig:pfs_freq}
\end{figure}

@@

\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{images/segmentation.png} 
    \caption{Differences between FNIRT results of one subject from PreFreeSurfer 
    (checkerboard image \emph{T2w\_acpc\_to\_MNI\_nonli.nii.gz}) (CentOS6 vs. 
    CentOS7). Right images show the zoomed version part of the images marked 
    by the red rectangle.
    Here is 
    \href{https://raw.githubusercontent.com/ali4006/HCP-reproducibility-paper/master/images/brain_classification.gif}
    {the link} to the gif animation of the same images.
} 
    \label{fig:fnirt_result}
\end{figure}

@@

\begin{figure}
%  \includegraphics{brain\_classification}
\centering
  \includegraphics[width=\columnwidth]{images/brain_classification_mni.png} 
  \caption{Heatmap binarized differences between brain segmentation results (file \emph{aseg.hires.mgz}) from 
          20 subjects in FreeSurfer (CentOS6 vs. CentOS7).
          We calculated some statistics of the differences based on the dice value of the segmented regions.
          Here is 
          \href{https://encsconcordiaca-my.sharepoint.com/:x:/g/personal/m_alari_encs_concordia_ca/EfNB-QMcivhIv6j0r9weffwBCHujf8RbaKjiYalIFa8cbQ?e=hyvQSU}
          {the link} to the excel file.} 
  \label{fig:tissue_class}
\end{figure}

@@

Although we identify the processes in the pipeline that create differences, 
the amplification of these differences should be quantified in the future works.
